\documentclass[a4paper,12pt]{article}

\usepackage{url}
\usepackage{parskip} 	

\RequirePackage{color}
\RequirePackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[scale=0.9]{geometry}

\usepackage{tabularx}

\usepackage{enumitem}

\newcolumntype{C}{>{\centering\arraybackslash}X} 

\usepackage{supertabular}
\usepackage{tabularx}
\newlength{\fullcollw}
\setlength{\fullcollw}{0.47\textwidth}

\usepackage{titlesec}				
\usepackage{multicol}
\usepackage{multirow}

\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{10pt}{10pt}

\usepackage[style=authoryear,sorting=ynt, maxbibnames=2]{biblatex}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}
\addbibresource{citations.bib}
\setlength\bibitemsep{1em}

\usepackage{fontawesome5}

\usepackage{tabto}    
\newcommand\mytab{\tab \hspace{-5cm}}

\begin{document}

\pagestyle{empty} 

\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{Danila Kurach} \\[7.5pt]
\href{https://github.com/dupreehkuda}{\raisebox{-0.05\height}\faGithub\ dupreehkuda} \ $|$ \ 
% \href{https://linkedin.com/in/dupreehkuda}{\raisebox{-0.05\height}\faLinkedin\ dupreehkuda} \ $|$ \ 
\href{https://t.me/dupreehkuda}{\raisebox{-0.05\height}\faTelegramPlane \ dupreehkuda} \ $|$ \ 
\href{mailto:danyakurach@gmail.com}{\raisebox{-0.05\height}\faEnvelope \ danyakurach@gmail.com} \ $|$ \ 
\href{tel:+7 (910) 406-17-73}{\raisebox{-0.05\height}\faMobile \ +7 (910) 406-17-73} \\
\end{tabularx}

\section{Summary}
Golang Backend developer with more than half a year learning experience. In the past, I have been making iOS apps with Swift and SwiftUI for a year. I'm interested in making the world a better place. Best motivated when seeing the impact on end users. In my spare time, I love learning new technologies and skills, playing chess, and reading books. 

\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}	
2020 - present & \textbf{Plekhanov University of Economics} \hfill Moscow, Russia \\ & Bachelor in Computer Science 
\end{tabularx}

\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Yandex Practicum} Go Developer (learning experience) & \hfill Jul 2022 - Oct 2022 \\[3.75pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
    \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
        \item[] Developed two projects during the course: \href{https://github.com/dupreehkuda/url-shortener}{url-shortener} and \href{https://github.com/dupreehkuda/Gophermart}{bonus accrual service}
        \begin{itemize}[nosep,after=\strut, leftmargin=1em, itemsep=3pt]
            \item[--] Url-shortener can process batches, compress responses with gzip, store data in memory/file/postgres, identify users with cookies
            \item[--] Bonus accrual service store data in postgres, identify users with JWT-tokens
        \end{itemize}
        \item[] Learned how to work with flags, environment variables, context, concurrency, error handling and table tests.
        % \item[--] Tech: Go, Gin, Postgres, pgx, JWT, Docker
    \end{itemize}
\end{minipage}
}
\end{tabularx}

%Projects
\section{Projects}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Service for managing user balance} & \hfill \href{https://github.com/dupreehkuda/transaction-service}{Link to Repo} \\[3.75pt]
\multicolumn{2}{@{}X@{}}{Developed a persistent service that manages accounts and uses queues for user requests. Queues are stored in file for service persistancy. Used fan-in like pattern. Tech: Go, Chi, Docker, Postgres}  \\
\end{tabularx}

\section{Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
Programming &  \normalsize{Go, Swift, TypeScript, Python, C++}\\
Frameworks &  \normalsize{Gin, Svelte}\\
Tools &  \normalsize{Postgres, MySQL, Docker, gRPC, Vim, Shell, Git}\\
Languages &  \normalsize{English - Professional Proficiency, Russian - Native Proficiency}\\  
\end{tabularx}

\vfill
\center{\footnotesize \today}

\end{document}
